Commutative character sheaves and geometric types for supercuspidal representations

### 2017-05-11 CJM/letter to CJM.tex
Added todonotes for CJM letter
Letter

\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}

@@

@@

{Regarding CJM: MS 1903 (Commutative character sheaves and geometric types for supercuspidal representations)} % subject of the letter

\begin{enumerate}
\item[(1)] We are extremely grateful for this observation. We had made a mistake. Fortunately, the correction had the effect of simplifying the constructions and did not add to the length of the paper. \todo{Should we say more?}
\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review. Our main motivation for Section 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups. (Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.
\end{enumerate}

>>>>

\usepackage{tikz}
\usetikzlibrary{shapes,arrows,calc,matrix}
\usepackage{tikz-cd}
\usepackage{todonotes}

@@

\noindent\textbf{Regarding CJM: MS 1903 (Commutative character sheaves and geometric types for supercuspidal representations)} % subject of the letter

\bigskip

@@

Thank you for sending us the review from the referee. We have now addressed all the comments, as summarized below. Allow us also to express our gratitude for such  insightful remarks and helpful comments.

Best  regards,

Clifton and David

\bigskip

\begin{enumerate}
\item[(1)] We are extremely grateful for this observation. We had made a mistake. Fortunately, the correction had the effect of simplifying the constructions and did not add to the length of the paper. We hope this change is clear in the attached version.
\item[(2)] It is quite true that it would be possible to view Section 4 as an application of our earlier paper, bypassing the the first part of the paper under review. Our main motivation for Section 1--3 was twofold: to address the `defect' in the dictionary from our earlier paper; and to extend that dictionary, as it pertains to characters, to non-commutative groups. (Although it wasn't our motivation, we were also happy to find an alternative to the stacky abelianization of Kamgarpour.) We have added a comment to this effect after Theorem 3.12, in the hopes that it will clarify this point.
\end{enumerate}
